\documentclass[master]{thesis-uestc}

\title{基于可信执行环境的高性能加密重复数据删除研究}{High-Performance Encrypted Data Deduplication System Based on TEE}
\author{任彦璟}{Ren Yanjing}
\setdate[submit]{2022年3月17日}
\setdate[oral]{2022年4月15日}  
\setdate[confer]{2022年6月8日} 
\advisor{李经纬\chinesespace 副教授}{Prof. Dr. Jingwei Li}
\school{计算机科学与工程学院(网络空间安全学院)}{School of Computer Science and Engineering(School of Cyberspace Security)}
\major{计算机科学与技术}{Computer Science and Technology}
\studentnumber{201921080334}
% \ProfessionalDegreeArea{随便学学}
\ClassificationNumber{TP309.2}
\ClassifiedClass{公开}
\UDCNumber{004.78}

\newcommand{\sysnameS}{\textrm{TEEDedup}\xspace}
\newcommand{\sysnameF}{\textrm{FeatureSpy}\xspace}
\newcommand{\prototype}{\textrm{TEEDedup+}\xspace}
% non-hanging indent 
\usepackage{enumitem}
\setenumerate{listparindent=\parindent, fullwidth,itemindent=2em,label=(\arabic*)}
\setitemize{listparindent=\parindent, fullwidth, itemindent=2em}
% \makeglossaries

\begin{document}
\makecover
\originalitydeclaration
\input{abstract}

\thesistableofcontents
% \thesisfigurelist
% \thesistablelist
% \glsaddall
% \thesisglossarylist


% Main body
\input{introduction}
\input{background}
\input{SGXDedup}
\input{FeatureSpy}
\input{summary}

\thesisacknowledgement
\input{acknowlegdegment}

\thesisbibliography[large]{reference}

\thesisappendix
\input{appendix}

% \begin{thesistheaccomplish}
%     \section{学术论文}
%     \bibitem{SGXDedup} 第一作者. Accelerating Encrypted Deduplication via SGX[C]. Proc.of USENIX ATC, 2021, 957-971. \textbf{CCF-A}
%     \bibitem{TED} 第三作者. Balancing storage efficiency and data confidentiality with tunable encrypted deduplication[C]. Proc. of EuroSys, 2020, 1-15. \textbf{CCF-B}
%     \bibitem{Metadedup} 学生第一作者. Metadedup: Deduplicating metadata in encrypted deduplication via indirection[C]. Proc. of MSST, 2019, 269-281. \textbf{CCF-B}
%     \bibitem{TEDExt} 第三作者. Tunable Encrypted Deduplication with Attack Resilient Key Management[J]. ACM Transactions on Storage (TOS), 2022. \textbf{CCF-A}
%     \bibitem{MetadedupExt} 第三作者. Enabling Secure and Space Efficient Metadata Management in Encrypted Deduplication[J]. IEEE Transactions on Computers (TC), 2021. \textbf{CCF-A}
%     \bibitem{Attack} 第四作者. Revisiting Frequency Analysis against Encrypted Deduplication via Statistical Distribution[C]. Proc. of IEEE INFOCOM, 2021. \textbf{CCF-A}
%     \section{发明专利}
%     \bibitem{CN111338572B} 第三发明人. 一种可调节加密重复数据删除方法:CN111338572B[P]. 2021-09-14.
%     \bibitem{CN110109617B} 第三发明人. 一种加密重复数据删除系统中的高效元数据管理方法:CN110109617B[P]. 2020-05-12.
%     \bibitem{CN112947855A} 第二发明人. 一种基于硬件安全区的高效加密重复数据删除方法:CN112947855A[P]. 2021-06-11.
%     \bibitem{CN112152798A} 第三发明人. 基于加密数据去重的分布式密文共享密钥管理方法及系统:CN112152798A[P]. 2020-12-29.
% \end{thesistheaccomplish}


\begin{thesistheaccomplish}
    \section{学术论文}
    \bibitem{SGXDedup} \textbf{Ren, Yanjing} and Li, Jingwei and Yang, Zuoru and Lee, Patrick PC and Zhang, Xiaosong. Accelerating Encrypted Deduplication via SGX[C]. Proc.of USENIX ATC, 2021, 957-971. \textbf{CCF-A}
    \bibitem{TED} Li, Jingwei and Yang, Zuoru and \textbf{Ren, Yanjing} and Lee, Patrick PC and Zhang, Xiaosong. Balancing storage efficiency and data confidentiality with tunable encrypted deduplication[C]. Proc. of EuroSys, 2020, 1-15. \textbf{CCF-B}
    \bibitem{Metadedup} Li, Jingwei and Lee, Patrick PC and \textbf{Ren, Yanjing} and Zhang, Xiaosong. Metadedup: Deduplicating metadata in encrypted deduplication via indirection[C]. Proc. of MSST, 2019, 269-281. \textbf{CCF-B}
    \bibitem{TEDExt} Yang, Zuoru and Li, Jingwei and \textbf{Ren, Yanjing} and Lee, Patrick PC and Zhang, Xiaosong. Tunable Encrypted Deduplication with Attack Resilient Key Management[J]. ACM Transactions on Storage (TOS), 2022. \textbf{CCF-A}
    \bibitem{MetadedupExt} Li, Jingwei and Huang, Suyu and \textbf{Ren, Yanjing} and Yang, Zuoru and Lee, Patrick PC and Zhang, Xiao-song and Hao, Yao. Enabling Secure and Space Efficient Metadata Management in Encrypted Deduplication[J]. IEEE Transactions on Computers (TC), 2021. \textbf{CCF-A}
    \bibitem{Attack} Li, Jingwei and Wei, Guoli and Liang, Jiacheng and \textbf{Ren, Yanjing} and Lee, Patrick PC and Zhang, Xiaosong. Revisiting Frequency Analysis against Encrypted Deduplication via Statistical Distribution[C]. Proc. of IEEE INFOCOM, 2021. \textbf{CCF-A}
    \section{发明专利}
    \bibitem{CN111338572B} 李经纬, 杨祚儒, \textbf{任彦璟}, 李柏晴, 张小松. 一种可调节加密重复数据删除方法:CN111338572B[P]. 2021-09-14.
    \bibitem{CN110109617B} 李经纬, 李柏晴, \textbf{任彦璟}, 张小松. 一种加密重复数据删除系统中的高效元数据管理方法:CN110109617B[P]. 2020-05-12.
    \bibitem{CN112947855A} 李经纬, \textbf{任彦璟}, 杨祚儒, 李柏晴, 张小松. 一种基于硬件安全区的高效加密重复数据删除方法:CN112947855A[P]. 2021-06-11.
    \bibitem{CN112152798A} 李经纬, 黄苏豫, \textbf{任彦璟}, 杨祚儒, 李柏晴. 基于加密数据去重的分布式密文共享密钥管理方法及系统:CN112152798A[P]. 2020-12-29.
\end{thesistheaccomplish}

\end{document}